---
title: "traitR documentation"
author: "Linley"
date: "June 28, 2016"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## TraitR

TraitR is the R version of traitspaces written by Steve Heard (initially in visualbasic). Chandra Moffit and I recoded it for R and I decided to shinyfy it. There are two versions: a standalone and the shiny app. Both will implement a pca for numeric data or a pcoa for a combination of numeric and categorical data. Categorical data can be factors or ordered factors. The pcoa implements the gower dissimilarity gowdis function in the FD package. The pca uses the primcomp function.

The code for the standalone is as follows:

source("traitR_standalone_pca_pcoa.R)
traitR.fun(df,speciescol,attackedcol,ancspecies,attackedgroup,traitgrp,niter,test="pca",correction=NULL)

df: a data frame to use
speciescol: the column name depicting the insect species
attackedcol: the column name designating attacked/unattacked
ancspecies: the designator for the ancestral species in speciescol
ancspecies: the designator for the attacked level in attackedcol
traitgrp: a list of column names giving the traits of interest. Easiest to generate using
  traitgrp<-list(mydat[,3:7])
niter: number of iteractions
test: either "pca" or "pcoa"
correction: for pcoa - "none", 



```{r pressure, echo=FALSE}
plot(pressure)
```

